---
title: "Couse 8 Project Quantified Self Movement"
author: "Autoz"
date: "2018.1.9"
output:
  html_document: default
  pdf_document: default
---
# Introduction

One thing that people regularly do is quantify
how much of a particular activity they do,
but they rarely quantify how well they do it.
In this project, your goal will be to use data
from accelerometers on the belt, forearm, arm,
and dumbell of 6 participants. With Following Steps,

`1 fit model`

`2 cross validation`

`3 sample errors`

`4 make choices`

`5 predict 20 test case`

# Load Data

```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(tidyverse)

training_raw <- read_csv("pml-training.csv",na = c("NA","#DIV/0!",""))
testing_raw <- read_csv("pml-testing.csv",na = c("NA","#DIV/0!",""))
training_raw <- as.data.frame(training_raw)
testing_raw <- as.data.frame(testing_raw)
```


# Cleaning the Training Data

<!-- Clean Data -->

```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
training_raw$classe <- factor(training_raw$classe)
```


# Remove columns with more than 70% of NA or "" values

```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
NArate <- function(x){
    apply(x, 2, function(y) sum(is.na(y)))/nrow(x)
}

training_raw <- training_raw[,NArate(training_raw) < .7]
```


# Remove near zero variances


```{r message=FALSE, warning=FALSE, paged.print=FALSE}
library(caret)
nzvCol <- nearZeroVar(training_raw, saveMetrics = TRUE)
training_raw <- training_raw[, !nzvCol$nzv]
```


# Remove unused variables


```{r}
training_raw <- training_raw[,-grep("name|timestamp|window|^X",names(training_raw))]

```


# Impute all NAs

```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(mice)
imp <- mice(training_raw,seed = 3)
training_raw <- mice::complete(imp)

```


# Remove 75% highly Correlative Variables  

```{r}
trainingNC <- training_raw[, -length(names(training_raw))]

findcor <- findCorrelation(cor(trainingNC,use="complete.obs"), cutoff = .75)

trainingFiltered <- training_raw[,-findcor]
trainingFilteredNC <- trainingNC[,-findcor]

```

<!-- Clean Data End -->

# Cross validation

```{r}
inTrain <- createDataPartition(y = trainingFiltered$classe, p = 0.75, 
                               list = FALSE) # 75% training
training <- trainingFiltered[inTrain,]
testing <- trainingFiltered[-inTrain,]

```

# Model Evaluation

# Regression Tree

```{r warning=FALSE}
library(rpart)
system.time(mod_rpart <- rpart(formula = classe ~ ., data = training))
predict_rpart <- predict(mod_rpart,newdata = testing,
                         type = "class")
confusionMatrix(predict_rpart,testing$classe)
```


# C50 Tree

```{r warning=FALSE}
library(C50)
system.time(mod_C50 <- C5.0(formula = classe ~ ., data = training))
predict_C50 <- predict(mod_C50,newdata = testing)
confusionMatrix(predict_C50,testing$classe)

```

# SVM

```{r warning=FALSE}
library(kernlab)
library(e1071)
system.time(mod_svm <- svm(formula = classe ~ ., data = training,
                           kernel = "linear",cost = 10))
predict_svm <- predict(mod_svm,newdata = testing)
confusionMatrix(predict_svm,testing$classe)
```


# Random forest

```{r warning=FALSE,cache = TRUE}
library(randomForest)
system.time(modrf <- randomForest(formula = classe ~ ., data = training))
predict_rf <- predict(modrf,newdata = testing)
confusionMatrix(predict_rf,testing$classe)
```


# Model verification

Using parallel acceleration because it's very consuming time in caret Random forest.

# Use Parallel CPU

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
library(parallel)
library(doParallel)
cluster <- makeCluster(detectCores() - 1) # convention to leave 1 core for OS
registerDoParallel(cluster)
```

# CV Random forest

```{r cache = TRUE}
set.seed(33)
fitControl <- trainControl(method = "cv",
                           number = 2,
                           classProbs = T,
                           preProcOptions = c("pca"),
                           verboseIter = T,
                           allowParallel = T)

system.time(mod_rf <- train(classe ~ ., data = training,
                            trControl = fitControl,
                            preProcess = c("center", "scale"),
                            method = "rf"))

predict_rf <- predict(mod_rf,newdata = testing)

confusionMatrix(predict_rf,testing$classe)

```


# Stop Parallel

```{r}
stopCluster(cluster)
registerDoSEQ()

```

# Final Result, Predict 20 Cases
```{r}
(final_result <- predict(modrf, testing_raw))
```

# Conclutions

Ramdon Forest Accuracy is 0.9927 and the best fit model of this case. So we choose Ramdon Forest to predict 20 cases.

# Appendix 

# Training Data Corrplot 

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(corrplot)
corrplot(cor(trainingNC,use="complete.obs"), method = "color", tl.cex = 0.5)
corrplot(cor(trainingFilteredNC,use="complete.obs"), method = "color", tl.cex = 0.5)
```

# Regression Tree Plot

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(rpart.plot)
prp(mod_rpart, extra=1, uniform=F, branch=1, yesno=F, border.col=0, xsep="/")
rpart.plot(mod_rpart, type=4, extra=0, branch.lty=3, box.palette = "auto",
           cex = .82)
```


